---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# KSIC

This package provides tools to utilize the Korea Standard Industrial Classification (KSIC) in R.

R에서 한국표준산업분류(KSIC)를 이용하기 위한 패키지입니다.

- Data: **ksicDB**, **ksicTreeDB**, **ksic_9_to_10**, **ksic_10_to_9**
- Function: **ksic()**, **is_ksic()**, **ksic_group()**, **ksic_sub()**

The data is sourced from:
데이터의 출처는 아래와 같습니다.

- [Korea Statistical Classification Portal (통계분류포털)](https://kssc.kostat.go.kr)

## Installation

You can install the KSIC package from GitHub with:
KSIC package는 아래와 같이 설치할 수 있습니다.

``` r
# install.packages("devtools")
devtools::install_github("jjyunnn/KSIC")
```

---

## Core Functions / 주요 함수

This package offers four main functions designed for efficiency and flexibility.
이 패키지는 효율성과 유연성을 고려하여 설계된 네 가지 주요 함수를 제공합니다.

### `ksic()`

Retrieves a `data.frame` of KSIC data filtered by a specific revision and digit level.
특정 차수와 자릿수 수준으로 필터링된 KSIC 데이터프레임을 가져옵니다.

**Example / 사용 예시:**
```{r}
ksic(digit = 1, C = 10)
```

### `is_ksic()`

Checks whether input codes are valid KSIC codes for the 9th and 10th revisions.
입력된 코드가 9차 및 10차 KSIC에서 유효한 코드인지 확인합니다.

**Example / 사용 예시:**
```{r}
is_ksic(c("A", "01", "99999", "invalid_code"))
```

### `ksic_group()`

Extracts the parent (upper-level) classification codes or names for a vector of KSIC codes.
주어진 KSIC 코드 벡터에 대한 상위 분류 코드 또는 이름을 추출합니다.

**Key Features & Advantages / 주요 특징 및 장점:**
- **Flexible Input**: Handles vectors with mixed-digit codes (e.g., `c("011", "2622")`).
- **유연한 입력**: 자릿수가 다른 코드들이 섞인 벡터(예: `c("011", "2622")`)도 처리할 수 있습니다.
- **Efficient**: Uses an optimized `split-lapply-unsplit` pattern for fast lookups.
- **효율성**: 최적화된 `split-lapply-unsplit` 패턴을 사용하여 빠른 조회를 보장합니다.

**Example / 사용 예시:**
```{r}
ksic_group(c("31311", "4631", "25"), digit = 2, name = TRUE)
```

### `ksic_sub()`

Extracts all child (lower-level) classification codes or names for a vector of KSIC codes.
주어진 KSIC 코드 벡터에 대한 모든 하위 분류 코드 또는 이름을 추출합니다.

**Key Features & Advantages / 주요 특징 및 장점:**
- **Comprehensive Output**: Returns a `list` where each element contains a vector of child codes.
- **포괄적인 출력**: 각 입력 코드에 해당하는 하위 코드 벡터를 담은 `리스트`를 반환합니다.
- **Flexible Input**: Handles vectors with mixed-digit codes.
- **유연한 입력**: 자릿수가 다른 코드가 섞인 벡터도 처리합니다.

**Example / 사용 예시:**
```{r}
result_list <- ksic_sub(c("26","96"), digit = 4)
print(result_list)
```

---

## Practical Application / 활용 사례

### Enriching a Dataset with `ksic_group`

You can easily use `ksic_group` to enrich your dataset by adding parent classifications.
`ksic_group`을 사용해 상위 분류 정보를 추가하여 데이터셋을 쉽게 확장할 수 있습니다.

```{r}
my_data <- data.frame(
  company = c("A", "B", "C", "D"),
  ksic5_cd = c("26222", "58221", "26299", "61220")
)

my_data$ksic2_nm <- ksic_group(my_data$ksic5_cd, digit = 2, name = TRUE)
print(my_data)
```

### Finding All Sub-Industries with `ksic_sub`

`ksic_sub` is useful for identifying all specific industries within a broader category. The list output can be easily converted into a tidy data frame for further analysis.
`ksic_sub`는 특정 상위 분류에 속하는 모든 세부 산업을 찾아낼 때 유용합니다. 리스트 형태의 출력 결과는 추가 분석을 위해 데이터프레임으로 쉽게 변환할 수 있습니다.

```{r}
# 분석할 중분류 코드 정의
# Define mid-level divisions for analysis
target_divisions <- c("58", "61") # 출판업, 우편 및 통신업

# ksic_sub를 사용하여 세세분류(5-digit) 코드와 코드명 찾기
# Use ksic_sub to find all 5-digit sub-category codes and names
sub_codes_list <- ksic_sub(target_divisions, digit = 5, name = FALSE)
sub_names_list <- ksic_sub(target_divisions, digit = 5, name = TRUE)

# --- Base R Approach ---
# Base R을 사용하여 리스트를 데이터프레임으로 변환
# Convert the list to a data.frame using Base R
sub_categories_df_base <- data.frame(
  ksic2_cd = rep(names(sub_codes_list), lengths(sub_codes_list)),
  ksic5_cd = unlist(sub_codes_list, use.names = FALSE),
  ksic5_nm = unlist(sub_names_list, use.names = FALSE)
)
cat("--- Using Base R ---\n")
print(head(sub_categories_df_base))

# --- Tidyverse Approach ---
# A more concise approach using the tidyverse (tidyr, tibble)
# tidyverse(tidyr, tibble)를 사용한 방법 (더 간결함)
# if (!require(tidyr)) install.packages("tidyr") 
# if (!require(tibble)) install.packages("tibble")

cat("\n--- Using Tidyverse ---\n")

# 1. Create a nested tibble where some columns are lists
# 1. 리스트를 열로 포함하는 중첩된 tibble 생성
nested_tibble <- tibble::tibble(
    ksic2_cd = names(sub_codes_list),
    ksic5_cd = sub_codes_list,
    ksic5_nm = sub_names_list
)
cat("\nStep 1: Nested tibble (before unnesting)\n")
print(nested_tibble)

# 2. Use tidyr::unnest() to expand the list-columns into regular rows
# 2. tidyr::unnest()를 사용하여 리스트 열을 일반적인 행으로 펼침
unnested_df <- tidyr::unnest(nested_tibble, cols = c(ksic5_cd, ksic5_nm))
cat("\nStep 2: Unnested tibble (final result)\n")
print(head(unnested_df))
